High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales

### 2021-03-11 inst/manuscript/manuscript.Rmd
Updated acknowledgements in MS, and added TOC and data availability statement to SI.

## Next steps
The maps presented here represent a version 1 product that is freely available to use, along with its underlying code. These data were developed according to the recommended best practices for training and assessing error in machine learning models [@ElmesAccountingtrainingdata2020]. In their current form, the maps may be useful for a variety of research applications. For example, analyzing the distributions of values in the probability maps may provide additional insight into the relative extents of active versus fallow croplands [@Tongforgottenlanduse2020]. However, use of these data, particularly for decision-making processes (e.g. cropped area estimates), should be careful to account for the reported errors [@OlofssonGoodpracticesestimating2014; @StehmanKeyissuesrigorous2019].

@@

# Acknowledgements
The primary support for this work was provided by Omidyar Network's Property Rights Initiative, now PLACE. Additional support was provided by NASA (80NSSC18K0158), and the National Science Foundation (SES-1801251; SES-1832393). Computing support was provided by the AWS Cloud Credits for Research program and the Amazon Sustainability Data Initiative. Azavea provided significant contributions in engineering the machine learning pipeline. We thank Meridia for providing initial information about local cropping systems and the characteristics of fields, and Radiant Earth Foundation for advice and guidance regarding machine learning best practices. We thank Manushi Trivedi, Sitian Xiong, and Tammy Woodard for their contributions to the underlying datasets and methods, and Michelle Gathigi, Omar Shehe, and Primoz Kovacic for support and management of the labelling efforts.

>>>>

## Next steps
The maps presented here represent a version 1 product that is freely available to use, along with its underlying code (see SI for details). These data were developed according to the recommended best practices for training and assessing error in machine learning models [@ElmesAccountingtrainingdata2020]. In their current form, the maps may be useful for a variety of research applications. For example, analyzing the distributions of values in the probability maps may provide additional insight into the relative extents of active versus fallow croplands [@Tongforgottenlanduse2020]. However, use of these data, particularly for decision-making processes (e.g. cropped area estimates), should be careful to account for the reported errors [@OlofssonGoodpracticesestimating2014; @StehmanKeyissuesrigorous2019].

@@

# Acknowledgements
The primary support for this work was provided by Omidyar Network's Property Rights Initiative, now PLACE. Additional support was provided by NASA (80NSSC18K0158), the National Science Foundation (SES-1801251; SES-1832393), and Princeton University. Computing support was provided by the AWS Cloud Credits for Research program and the Amazon Sustainability Data Initiative. Azavea provided significant contributions in engineering the machine learning pipeline. We thank Meridia for providing information about local cropping systems and the characteristics of fields, and Radiant Earth Foundation for advice and guidance regarding machine learning best practices. We thank Manushi Trivedi, Sitian Xiong, and Tammy Woodard for their contributions to the underlying datasets and methods, and Michelle Gathigi, Omar Shehe, and Primoz Kovacic for support and management of the labelling efforts.

### 2021-03-11 inst/manuscript/si.Rmd
Updated acknowledgements in MS, and added TOC and data availability statement to SI.

output:
  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: no
    extra_dependencies: ["float", "titling", "setspace"]
    includes:
      in_header: header.tex

@@

# Methods
## Assessing quality of composites
The rubric presented in Table \ref{tab:imqcriteria} was used to assess the quality of the seasonal image composites. The imagery was evaluated by examining their Raster Foundry [@azaveaRasterFoundry2020] overlays within a `labeller` instance set up for the purpose.

@@

# Results
## Image catalog and quality

@@

>>>>

output:
  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: yes
    toc_depth: 4
    toc: yes
    extra_dependencies: ["float", "titling", "setspace"]
    includes:
      in_header: header.tex

@@

# Supplemental Methods
## Assessing quality of composites
The rubric presented in Table \ref{tab:imqcriteria} was used to assess the quality of the seasonal image composites. The imagery was evaluated by examining their Raster Foundry [@azaveaRasterFoundry2020] overlays within a `labeller` instance set up for the purpose.

@@

# Supplemental Results
## Image catalog and quality

@@

# Code and Data Availability
The repositories containing the data, code, and manuscript source files used to produce this paper are listed below:

- [`activemapper`](https://github.com/agroimpacts/activemapper): Contains the source code and derived data for this paper. The repository\footnote{github.com/agroimpacts/activemapper} will be opened following publication in a peer-reviewed journal.
- [`croplandmaps`](https://github.com/agroimpacts/croplandmaps_V2): Source code for web map displaying image composites and cropland probability maps. The repository\footnote{github.com/agroimpacts/croplandmaps\_V2} is open, and the field boundary datasets are available for download. 
- [`imager`](https:github.com/agroimpacts/imager): Source code for the image processing software. The repository\footnote{github.com/agroimpacts/imager} is currently private, but will be opened after completing a security audit. 
- [`labeller`](https:github.com/agroimpacts/labeller): Source code for the labelling platform. The repository\footnote{github.com/agroimpacts/labeller} is currently private, but will be opened after completing a security audit. 
- [`learner`](https:github.com/agroimpacts/learner): Source code for the active learning component. The repository\footnote{github.com/agroimpacts/learner} is open.
- [`segmenter`](https:github.com/agroimpacts/segmenter): Source code for the segmentation algorithm. The repository \footnote{github.com/agroimpacts/segmenter} is currently private, but will be opened after completing a security audit.
